---
title: "Regular Expressions"
author: "Atta Boateng"
date: "02-011-2024"
output: 
  html_document:
    figure_caption: yes

---

### 1. 

  Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r echo=TRUE, results='asis'}
library(knitr)
library(stringr)

path <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv";
download.file(url=path, destfile = "majors-list.csv");

majors <- read.csv("majors-list.csv", stringsAsFactors = FALSE);


kable(str_subset(majors$Major,pattern="DATA|STATISTICS"))
```

### 2.
  Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r echo=TRUE, results='asis'}
library(knitr)
library(stringr)

blob <- '"bell pepper"  "bilberry"     "blackberry"   "blood orange"
"blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
"elderberry"   "lime"         "lychee"       "mulberry"    
"olive"        "salal berry" '

scan(text=blob, what="character")

```

#3 

Describe, in words, what these expressions will match:

(.)\1\1  - singly repeat characters are matched
"(.)(.)\\2\\1" - words in reverse
(..)\1 - the first two characters are the same
"(.).\\1.\\1"- matches first character is at the beginning middle and end of the word
"(.)(.)(.).*\\3\\2\\1" - matches a word that has it's first three characters in reverse

#4 

Construct regular expressions to match words that:

Start and end with the same character. 
"^([a-z]).*\1$"
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
"([a-z][a-z]){1,}"
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.) "[a-z]{3,}"
